\section{Appendix: Http Status Codes Summary}
\label{appendix:http_status_codes_summary_appendix}

\begin{longtable}{@{}>{}l >{\raggedright\arraybackslash}p{5cm} >{\raggedright\arraybackslash}p{8cm}@{}}
    \caption{HTTP Status Codes Summary} \label{tab:http-status-codes} \\
\toprule
\textbf{HTTP Status Code} & \textbf{Name} & \textbf{Description} \\
\midrule
\endfirsthead

\multicolumn{3}{c}{\textbf{\tablename\ \thetable{} -- Continued from previous page}} \\
\toprule
\textbf{HTTP Status Code} & \textbf{Name} & \textbf{Description} \\
\midrule
\endhead

\midrule
\multicolumn{3}{r}{\small\textit{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot

100 & CONTINUE & Initial part of request received, not yet rejected by server. \\ \hline
101 & SWITCHING PROTOCOLS & Server agrees to change application protocol. \\ \hline
200 & OK & Request has succeeded. \\ \hline
201 & CREATED & Request fulfilled, new resources created. \\ \hline
202 & ACCEPTED & Request accepted but processing not completed. \\ \hline
203 & NO AUTHORITATIVE INFORMATION & Content modified by transforming proxy. \\ \hline
204 & NO CONTENT & Request succeeded, no additional content. \\ \hline
205 & RESET CONTENT & Request fulfilled, user agent should reset view. \\ \hline
206 & PARTIAL CONTENT & Server fulfilling range request. \\ \hline
300 & MULTIPLE CHOICES & Multiple representations available for resource. \\ \hline
301 & MOVED PERMANENTLY & Resource assigned new permanent URI. \\ \hline
302 & FOUND & Resource temporarily under different URI. \\ \hline
303 & SEE OTHER & Redirect to different resource for indirect response. \\ \hline
304 & NOT MODIFIED & Conditional request condition evaluated false. \\ \hline
305 & USE PROXY & No longer in use. \\ \hline
306 & (UNUSED) & No longer in use. \\ \hline
307 & TEMPORARY REDIRECT & Resource temporarily under different URI. \\ \hline
308 & PERMANENT REDIRECT & Resource assigned new permanent URI. \\ \hline
400 & BAD REQUEST & Server cannot process due to client error. \\ \hline
401 & UNAUTHORIZED & Lacks valid authentication credentials. \\ \hline
402 & PAYMENT REQUIRED & No current use. \\ \hline
403 & FORBIDDEN & Server understood but refuses to fulfill. \\ \hline
404 & NOT FOUND & No current representation for target resource. \\ \hline
405 & METHOD NOT ALLOWED & Method known but not supported. \\ \hline
406 & NOT ACCEPTABLE & No acceptable representation available. \\ \hline
407 & PROXY AUTHENTICATION REQUIRED & Client needs to authenticate with proxy. \\ \hline
408 & REQUEST TIMEOUT & Server did not receive complete request. \\ \hline
409 & CONFLICT & Conflict with current state of resource. \\ \hline
410 & GONE & Access no longer available (likely permanent). \\ \hline
411 & LENGTH REQUIRED & Server refuses without Content-Length. \\ \hline
412 & PRECONDITION FAILED & Request header conditions evaluated false. \\ \hline
413 & CONTENT TOO LARGE & Request content too large. \\ \hline
414 & URI TOO LONG & URI too long. \\ \hline
415 & UNSUPPORTED MEDIA TYPE & Content format not supported. \\ \hline
416 & RANGE NOT SATISFIABLE & Requested ranges not satisfiable. \\ \hline
417 & EXPECTATION FAILED & Expect header field could not be met. \\ \hline
418 & (UNUSED) & No longer in use. \\ \hline
421 & MISDIRECTED REQUEST & Server unable to produce authoritative response. \\ \hline
422 & NON-PROCESSABLE CONTENT & Unable to process contained instructions. \\ \hline
426 & UPGRADE REQUIRED & Server refuses with current protocol. \\ \hline
500 & INTERNAL SERVER ERROR & Unexpected condition prevented fulfillment. \\ \hline
501 & NOT IMPLEMENTED & Server lacks required functionality. \\ \hline
502 & BAD GATEWAY & Invalid response from upstream server. \\ \hline
503 & SERVICE UNAVAILABLE & Temporary overload or maintenance. \\ \hline
504 & GATEWAY TIMEOUT & No timely response from upstream server. \\ \hline
505 & HTTP VERSION NOT SUPPORTED & HTTP version not supported. \\

\end{longtable}
\label{tab:summary_http_status_codes}
\centering
\footnotesize Source: \cite{rfc9110}.